---
title: "Project -4 Text Mining"
author: "Arun Reddy"
date: "April 14, 2019"
output:
  html_document:
    toc: true
    toc_float: true
    Collapsed: false
    code_folding: show
    theme: flatly
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This is project is about demonstration of text classification into spam/ham using the Naive Bayes Machine Learning model.
The dataset is collected from SMS spam collection from [UCI Machine Learning Repository]("https://archive.ics.uci.edu/ml/datasets/SMS+Spam+Collection")
The dataset is segregated into two categories one is spam and other is ham. 
We will be using 80% of the dataset as a training set and rest as test set.
# Import Libraries


```{r message=FALSE, warning=FALSE,paged.print=FALSE}
library(tm)
library(SnowballC)
#library(wordcloud)
library(RColorBrewer)
library(e1071) # for Naive Bayes
library(caret) # for Confusion Matrix
```


# Data Import and Exploration

## Data Import

```{r message= FALSE}
# Import data
sms_raw<- read.csv("https://raw.githubusercontent.com/DataScienceAR/Cuny-Assignments/master/Data-607/Data-Sets/SpamHamText.csv")
head(sms_raw)


```

## Data Cleansing

### Subsetting the columns and rename the columns

```{r}

sms_raw <- sms_raw[, 1:2] # Fist column gives whether the observation is spam or ham and second column is the actual message
colnames(sms_raw) <- c("Tag", "Msg")
```

### Dataset breakdown by categories

```{r}
# Number of rows and columns
dim(sms_raw)

# Number or % of Spam and Ham messages
table(sms_raw$Tag)
prop.table(table(sms_raw$Tag))

```

#### Data processing

```{r}
sms_corpus <- VCorpus(VectorSource(sms_raw$Msg))

sms_dtm <- DocumentTermMatrix(sms_corpus, control = 
                                 list(tolower = TRUE,
                                      removeNumbers = TRUE,
                                      stopwords = TRUE,
                                      removePunctuation = TRUE,
                                      stemming = TRUE))

dim(sms_dtm)
```

#### Creating Training and Test Data

```{r}
#Training & Test set
sms_dtm_train <- sms_dtm[1:4457, ]
sms_dtm_test <- sms_dtm[4458:5572, ]

#Training & Test Label
sms_train_labels <- sms_raw[1:4457, ]$Tag
sms_test_labels <- sms_raw[4458:5572, ]$Tag

#Proportion for training & test labels
prop.table(table(sms_train_labels))

prop.table(table(sms_test_labels))

threshold <- 0.1

min_freq = round(sms_dtm$nrow*(threshold/100),0)

min_freq
# Create vector of most frequent words
freq_words <- findFreqTerms(x = sms_dtm, lowfreq = min_freq)


#Filter the DTM
sms_dtm_freq_train <- sms_dtm_train[ , freq_words]
sms_dtm_freq_test <- sms_dtm_test[ , freq_words]

dim(sms_dtm_freq_train)

convert_values <- function(x) {
  x <- ifelse(x > 0, "Yes", "No")
}

sms_train <- apply(sms_dtm_freq_train, MARGIN = 2,
                   convert_values)
sms_test <- apply(sms_dtm_freq_test, MARGIN = 2,
                  convert_values)

```

# Naive Bayes Model Training

```{r}
#Create model from the training dataset
sms_classifier <- naiveBayes(sms_train, sms_train_labels)

#Make predictions on test set
sms_test_pred <- predict(sms_classifier, sms_test)

#Create confusion matrix
confusionMatrix(data = sms_test_pred, reference = sms_test_labels,
                positive = "spam", dnn = c("Prediction", "Actual"))
```

#Conclusion

We see that the model translated 5 spam messages as ham. The model is shows the accurancy of 98.12%.




