---
title: "Assignment Wk-2"
author: Arun Reddy
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc: true
    toc_float: true
    Collapsed: false
    code_folding: hide

---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Assignment Description
The purpose of the assigment is to create a movie table on a cloud database and retrieve the data from R code.
Create text file consisting of movie names and the ratings with the related attributes. Once created, load the data into a online cloud mySQL database and query the table in the R code and display the results


## R packages used

1. tidyr
2. dplyr
3. DT
4. RMySQL
5. DBI


```{r}
suppressMessages(library(tidyr))
suppressMessages(library(dplyr))
suppressMessages(library(DT))
suppressMessages(library(RMySQL))
suppressMessages(library(DBI))
```

## Raw movie file on .csv format

The file contains list of Netflix movies with different ratings. The file is updated on GitHub here 


 (https://raw.githubusercontent.com/DataScienceAR/silver-octo-funicular/master/Netflix%20Shows.csv)


```{r}
theurl <- url('https://raw.githubusercontent.com/DataScienceAR/silver-octo-funicular/master/Netflix%20Shows.csv')
movies.df <- tbl_df(read.csv(theurl))
datatable(head(movies.df,3))
```



## Creating Movie database and tables on Google Cloud

A new "Movie" database and tables are created in Google Cloud. The .csv files available on GitHub is used a source to feed the table creation.
Two tables are created under "Movie" Database.
Calling the SQL in R

```{r}
con <- dbConnect(RMySQL::MySQL(),
                 dbname = "Movies",
                 host = "34.73.184.91",
                 port = 3306,
                 user = "Ruser",
                 password = "Ruser"
                 
              
                 
                 )

```
### Querring the list of table in the "Movie" database

```{r}
dbListTables(con)
```
### Querring the "NetflixShows" table for top 5 rows

```{r}
dbGetQuery(con,"select * from `NetflixShows` limit 5 ")
```

### Get the list of observations that have user rating score greater than 97

```{r}
datatable(dbGetQuery(con,"SELECT
	nt.title `Movie Name`,
	nt.rating `Rating`,
	nt.ratingLevel `Rating Level`,
	nt.ratingDescription,
	nt.`release year` `Release Year` 
FROM
	`NetflixShows` nt 
	WHERE `user rating score` >97"))
```
### Get the count of movies by year that are more than 1 in count.

```{r}
dbGetQuery(con,"SELECT
	
		nt.`release year` `Release Year` ,
	COUNT(DISTINCT nt.title) `Movie Name`
FROM
	`NetflixShows` nt 
	WHERE `user rating score` >90


	GROUP BY 	
	
	nt.`release year` 
	HAVING COUNT(DISTINCT nt.title) >1
	ORDER BY
	`release year` DESC")
```



