---
title: "Assignment Wk-3"
author: Arun Reddy
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc: true
    toc_float: true
    Collapsed: false
    code_folding: hide

---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```




## R packages used

1. stringr


```{r}
suppressMessages(library(stringr))

```

# Question 3 Raw Data

Copy the introductory example. The vector name stores the extracted names. R> name [1] “Moe Szyslak” “Burns, C. Montgomery” “Rev. Timothy Lovejoy” [4] “Ned Flanders” “Simpson, Homer” “Dr. Julius Hibbert”


```{r}
raw.data <-"555-1239Moe Szyslak(636) 555-0113Burns, C. Montgomery555-6542Rev. Timothy Lovejoy555 8904Ned Flanders636-555-3226Simpson, Homer5553642Dr. Julius Hibbert"
Extracted.names <- unlist(str_extract_all(raw.data, "[[:alpha:]., ]{2,}"))
Extracted.names
```



## Question 3.1
Use the tools of this chapter to rearrange the vector so that all elements conform to the standard first_name last_name.
Stringr was used to combine steps into a single line of code.

```{r}
Std.FullName<-str_trim(sub("([^,]+),([^,]+)","\\2 \\1", sub("[[:alpha:].]{1,3}\\. ","",Extracted.names)))
Std.FullName

```
## Question 3.2
Construct a logical vector indicating whether a character has a title (i.e., Rev. and Dr.)

```{r}
Title<-str_detect(Extracted.names,"[[:alpha:].]{2,3}\\. ")
cbind(Extracted.names,Title)
```
## Question 3.3
Construct a logical vector indicating whether a character has a second name.
```{r}
MiddleName<-str_detect(Extracted.names," [[:alpha:].]{1}\\. ")
cbind(Extracted.names,MiddleName)
```

# Question 4
Describe the types of strings that conform to the following regular expressions and
construct an example that is matched by the regular expression.

## Question 4.1  - String containing '$' symbols
[0-9]+\\$

```{r}
str4.1 <- c("$4","$40","4$","40$30","30$","56 $")
str_detect(str4.1,'[0-9]+\\$')
```
## Question 4.2  - String of words containing length 1 -4 
\\b[a-z]{1,4}\\b  

```{r}
str4.2 <- c("four times four sixteen","aim high"," t ",'attt')
str_detect(str4.2,'\\b[a-z]{1,4}\\b')
```

## Question 4.3  - String with file name ending in .txt
.*?\\.txt$ 

```{r}
str4.3 <- c("File Format.txt","String Manipulation using stringR.txt","books.html","filename.php")
str_detect(str4.3,'.*?\\.txt$')
```

## Question 4.4  - String with a date format in the form of MM/DD/YYYY or DD/MM/YYYY
\\d{2}/\\d{2}/\\d{4}

```{r}
str4.4 <- c("01/22/2019","22/01/2019")

str_detect(str4.4,"\\d{2}/\\d{2}/\\d{4}")
```
## Question 4.5  - String with html tags
<(.+?)>.+?</\\1>

```{r}
str4.5 <- c("<p>Some HTML</p>","<p>Hello, <b>World</b>")
str_detect(str4.5,"<(.+?)>.+?</\\1>")
```
# Question 9  - Bonus Question

The following code hides a secret message. Crack it with R and regular expressions.
Hint: Some of the characters are more revealing than others! The code snippet is also
available in the materials at www.r-datacollection.com.
```{r}
str9 <-"clcopCow1zmstc0d87wnkig7OvdicpNuggvhryn92Gjuwczi8hqrfpRxs5Aj5dwpn0Tanwo
Uwisdij7Lj8kpf03AT5Idr3coc0bt7yczjatOaootj55t3Nj3ne6c4Sfek.r1w1YwwojigO
d6vrfUrbz2.2bkAnbhzgv4R9i05zEcrop.wAgnb.SqoU65fPa1otfb7wEm24k6t3sR9zqe5
fy89n6Nd5t9kc4fE905gmc4Rgxo5nhDk!gr"

str_replace_all(str9,"([a-z])|([0-9])|\n","")
```











