---
title: "Project 1- Data Cleansing & Analysis DataSet 1
"
author: Arun Reddy
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc: true
    toc_float: true
    Collapsed: false
    code_folding: show
   
   
    

---





```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
***
### Overview {.tabset .tabset-fade .tabset.-pills}
The dataset provided contains student information on 395 students including their grades in the class.



***
#### R Packages Used

This assignment was accomplished by utilizing these packages for both data analysis and visualizations.
```{r message=FALSE, warning=FALSE, paged.print=FALSE}

library("tidyr")
library("dplyr")
library("kableExtra")
library("ggplot2")
library("stringr")
library("lubridate")



```
***
#### The DataSet

The data is captured in the .csv format and updated into GitHub. You will see below that the data is not in a very clean form to conduct analysis easily, therefore this data set needed to be tidy.

```{r}
theURL <- "https://raw.githubusercontent.com/DataScienceAR/Cuny-Assignments/master/Data-607/Data-Sets/Students.csv"
RawFile <-data.frame(read.csv(file = theURL,header = TRUE))

#Table Structure
glimpse(RawFile)

#Top 6 rows of the table

head(RawFile)

```
***

### Data Manipulation {.tabset .tabset-fade .tabset.-pills}
The data needs to be cleaned and manipulated for it to be presentable for analysis.

***

#### Cleaning the table

* Transform the data type of some of columns to right data type 
```{r}
# Transform the data type of some of columns to right data type
RawFile$Student.ID <- as.character(RawFile$Student.ID)
RawFile$Medu <- as.factor(RawFile$Medu)
RawFile$Fedu <- as.factor(RawFile$Fedu)
RawFile$nurse_visit <- as.character(RawFile$nurse_visit)


```

***
* Padding the student id to make is 4 digit number 
```{r}

RawFile$Student.ID <-str_pad(RawFile$Student.ID, width = 4,side="left",pad = "1")
names(RawFile)[names(RawFile) =='Student.ID'] <- "Student_ID"



```

***
* Replace the codes with descriptions 
```{r}
RawFile$sex <- str_replace_all(RawFile$sex,"M","Male")
RawFile$sex <- str_replace_all(RawFile$sex,"F","Female")


```


***
* Select the required variables for analysis 
```{r}
head(RawFile)
TidyFile <-RawFile %>% select(Student_ID,sex,Mjob,Fjob,guardian,traveltime,studytime,freetime,absences)
dim(TidyFile)

```

### Data Analysis {.tabset .tabset-fade .tabset.-pills}

#### Untidy DataSet
***
 
```{r}
head(RawFile,10)


```

#### Tidy DataSet
***
 
```{r}
head(TidyFile,10)


```

#### Analysis
***
 
```{r}
subset_absence<-TidyFile %>% select(sex,guardian,absences) %>% group_by(sex,guardian) %>% summarise(Total=sum(absences))

barplot(subset_absence$Total)

```


















